Constant-sized correlations are sufficient to robustly self-test maximally entangled states with unbounded dimension

### 2019-08-02 Draft/draft.tex
Changes to section 5 and section 6.1

\begin{abstract}
	We show that for any prime odd integer $d$ with primitive $r$, there exists a correlation of size
	$\Theta(r^2)$ 
	that can robustly self-test a maximally entangled state of dimension $4d-4$. Our result is
	inspired by the robust self-testing result by Bamps and Pironio (\textit{Physical Review A} $91.5$ $(2015)$) and
	techniques introduced by Slofstra (\textit{Forum of Mathematics, Pi}. Vol. $7$, $2019$). Since there are
	infinitely many prime numbers with primitive root at most $5$ (\textit{The Mathematical Intelligencer} $10.4$ ($1988$)), 
	our result implies that constant-sized correlations are sufficient for robust self-testing of maximally entangled states
	with unbounded local dimension.
\end{abstract}
%========================================
\section{Introduction}
\label{sec:intro}
%========================================
Self-testing is a unique phenomenon of quantum mechanics. It has many applications in quantum
delegated computation \cite{ruv2013,coladan2017verifier} and device independent quantum cryptography
\cite{mayersyao,vv2014,miller2017,fu2018,eat2018}.
\carl{Two possible papers that you could cite are Mayer Yao 1998 (which originated the idea of self-testing as far as I know, and mentions QKD) and my paper (miller2017, which you've already cited --- indeed it uses the concept of self-testing).  Also you should check Vazirani-Vidick's 2014 PRL paper to see if it mentions self-testing at all.  (It was the first to fully prove DI-QKD.)}
\hfc{checked.}

The case of self-testing $2$-dimensional EPR pair is fully understood.
The techniques for robustly self-testing one EPR pair is 
first introduced in Ref.~\cite{mckague2012}, then improved in Ref.~\cite{bamps2015}. 
Ref.~\cite{yang2013} started to think about how to robustly self-testing large dimensional maxially entangled states.
Its ideas are realized later in Ref.~\cite{coladan2017all}, which proved that all pure bipartite entangled state 
can be self-tested.
One can also self-test many copies of the $2$-dimensional EPR
pair in parallel \cite{mckague2016,natarajan2017,coladan2016parallel}.
The most efficient way uses $O(\log n)$ bits question and
answers to self-test $n$ copies of $2$-dimensional EPR
pair \cite{lowdegree}.
\carl{I believe the first to prove robust self-testing of a single EPR pair was McKague-Yang-Scarani 2012.}
\hfc{Got it.}
Self-testing general $d$-dimensional EPR pairs is a harder task.
Coladangelo, Goh and Scarani has shown that all pure bipartite entangled states can be self-tested \cite{coladan2017all}
by constructing an explicit correlation of size $\Theta(d^2)$ that can be used for self-testing,
which is the only result about the general $d$-dimensional case so far.
However, proving the robustness of the correlation remains an open problem. 
Without robustness, we cannot infer anything about a quantum strategy if
the produced correlation deviates from the ideal correlation, no matter how small the 
deviation is.

A natural question to ask is whether maximally entangled states with large local dimension
can be self-tested with constant-sized correlations. 
In this paper, we give an affirmative answer to this question by proving the following theorem.
\begin{theorem}[Informal]
\label{thm:inf}
	There exists an infinite-sized set $D$ of odd prime numbers such that, for any $d \in D$, 
	the maximally entangled state of local dimension $4d-4$ can be robustly self-tested 
	with constant-sized question and answer alphabets.
\end{theorem}
The formal statement of this theorem is given in \cref{thm:self-test} and \cref{thm:infty}.

The set $D$ is, \carl{
specifically, the set of all 
odd prime numbers whose smallest primitive root is either $2$, $3$,
or $5$}.  It has been shown that \carl{this set} has infinitely many elements \cite{murty1988}.
To prove \cref{thm:inf}, we construct a correlation of size $\Theta(r^2)$ for each $d \in D$ whose primitive
root is $r$. This correlation is denoted by $\fC(d,r)$.
Note that although the size of $\fC(d,r)$ does not depend on $d$, the entries of $\fC(d,r)$ do.
Then we prove the robust self-testing property of $\fC(d,r)$ by showing 
that if some quantum strategy can approximate $\fC(d,r)$, then
the generalized swap isometry \cite{yang2013}
can produce the desired maximally entangled states when applied to the unknown state used in the strategy.
%Then the self-testing property of this correlation is 
%given in the following theorem.
%\begin{theorem}[Informal]
%\label{thm:pr_2}
%	All maximally entangled state with local dimension $d-1$, where $d$ is prime and has
%	primitive root $r \in \{2, 3, 5\}$, can be self-tested by a constant-sized correlation.
%\end{theorem}
\carl{The paper \cite{bamps2015} says that the earlier paper \cite{yang2013} has ``flaws.'' Check what those flaws are, and make sure that they won't put a shadow on anything that you're discussing when you cite \cite{yang2013}.}

In order to accomplish our goal, we first design a linear system game to enforce the 
relation $UOU\ct = O^r$, which is a generalization of a relation in Ref.~\cite{slofstra2017}.  \carl{A reader may get lost at the last sentence -- you're jumping into the material too quickly without enough explanation.}
The number of variables and the number of equations of the linear system game depend linearly on $r$,
which makes our correlation of size $\Theta(r^2)$.
Unlike previous self-testing proofs, which try to enforce the anti-commutation relation
$XZ = \omega_d^{-1} ZX$ between Pauli operators of dimension $d \geq 2$, 
our approach is more succinct in terms of the size of the correlation but at a cost that
it only works for odd prime $d$.
The reason why we focus on this relation is that if we can certify that $O$ has one eigenvalue $\omega_d$
for some $d$ with primitive $r$,
then it guarantees that $O$ has eigenvalues $\omega_d^j$ for $j = 1 \dots d-1$ and $U$ only
permutes the eigenvectors of $O$ in certain way.
After knowing the eigenvalues of $O$, we can use infer the structure of the shared state $\ket{\psi}$
based on the two relation of $\ket{\psi}$ imposed by the linear system game --
$U_A \x U_B \ket{\psi} = \ket{\psi}$ and $O_A \x O_B \ket{\psi} = \ket{\psi}$.
The two relations imply that $\ket{\psi}$ is spanned by eigenvectors of $O$ and its
Schmidt coefficient follows some pattern that is invariant under the permutation by $U$.
At this point, we can use the generalized swap isometry \cite{yang2013} to extract a copy of the 
$(d-1)$-dimensional maximally entangled state. Note that our robust self-testing proof 
follows a different line of arguments from what was originally
proposed in Ref.~\cite{yang2013}.
Our self-testing proof actually certifies $\ket{\EPR{2}}^{\x 2} \x \ket{\EPR{d-1}}$. 
The self-testing of $\ket{\EPR{2}}^{\x 2}$ follows a known result \cite{wu2016}.

The remaining question is how to certify a particular eigenvalue of $O$. Before going to the answer,
we remark that 
the other specialty of the linear system game is that it forces Alice and Bob to have binary observables
whose products are the special unitaries $U$ and $O$, because the answers to the questions of the 
linear system games are binary. 
The idea of decompose the unitaries of arbitrary order into binary observables was also first introduced by Slofstra \cite{slofstra2017}.
We use a different way to decompose the unitaries, which can be seen as the inverse of Jordan's lemma, 
The fact that Alice and Bob only have binary observables make it easier for us 
to compose the linear system game with another nonlocal test, which we call the extended weighted CHSH test.
The difference between a nonlocal game and a nonlocal test will be discussed later.
The core idea of the extended weighted CHSH test is to certify that Alice and Bob's observables and state 
for the linear system game can also be used to violate the weighted CHSH inequality \cite{acin2012} maximally.
We find that the maximal violation of the weighted CHSH inequality can certify the eigenvalues of the product
of Bob's observables. 
At this point, we fix a prime $d$ by picking the weight in the weighted CHSH inequality and 
use the extended weighted CHSH test to certify that
$O$ has eigenvalue $\omega_d$.
\carl{This paragraph (also) will need more context.}

@@

A quantum strategy of a nonlocal game or a nonlocal test presented in terms of projective measurements
consists of projective measurements $\{\{M_x^a\}_{a \in \calA_x} \}_{x \in \calX}$ on Alice's side, 
$\{\{N_y^b\}_{b \in \calB_y} \}_{y \in \calY}$ on Bob's side, and a shared state $\ket{\psi}$. 
By projective measurements, we mean that  
$(M_x^a)^2 = M_x^a = (M_x^a)^\dagger$ and $(N_y^b)^2 = N_y^b = (N_y^b)^\dagger$.
Then Alice and Bob's quantum strategy produces the conditional probability distribution
\begin{align}
	\pr{ab}{xy} = \bra{\psi} M_x^a \x N_y^b \ket{\psi},
\end{align}
for each $(x,y) \in \calX \times \calY$ and $(a,b) \in \calA_x \times \calB_y$.
Note that the tensor product structure indicates that the
two parties cannot communicate with each other, which is the reason why such game is called a nonlocal game.
For simplicity we omit the tensor product symbol between operators acting on different Hilbert spaces in the rest of the work, so if $M_x^a : \calH_A \rightarrow \calH_A$ and $N_y^b: 
\calH_B \rightarrow \calH_B$, then $M_x^a N_y^b: \calH_A\x \calH_B \rightarrow \calH_A \x \calH_B$.
\begin{definition}
	Given input alphabets: $\calX$ and $\calY$, and families of output
	alphabets: $\{\calA_x\}_{x \in \calX}$ and $\{\calB_y\}_{y \in \calY}$, a correlation is a family of conditional probability distributions
	$\{\pr{ab}{xy}: a \in \calA_x, b \in \calB_y\}_{x \in \calX, y \in \calY}$.  
\end{definition}
A particular type of nonlocal games that we are interested in is called binary linear system games.
\begin{definition}[Binary linear system game]
 Let \hf{$Hx = c$} be an $m \times n$ system of linear equations over $\Z_2 = \{0, 1\}$ (meaning that $H$ is an $m$-by-$n$ matrix with entries in $\Z_2$ and 
 $c$ is a length-$n$ vector with entries in $\Z_2$). 
 The associated linear system game involves two
 players Alice and Bob. 
 The input and output alphabets are 
 \begin{align*}
     \calX = \{I_i\}_{i=1}^m && \calY = \{1 \dots n\} \\
     \calA_{I_i} = \Z_2^{|I_i|} && \calB = \Z_2,
 \end{align*}
 where $I_i = \{j : H(i,j) = 1\}$.
 When Alice and Bob answer with $\ba$ and $b$ for questions $I_i$ and
 $j$ respectively,
 the scoring functions are defined by
 \begin{align}
 	V_{(I_i,j)}(\ba, b) =
	\begin{cases}
		1, \quad \text{if } \sum_{k \in I_i} H(i,k) a(k) \equiv c(i) \pmod 2 \text{ and } a(j) = b \\
		0,  \quad \text{otherwise.}
	\end{cases}
\end{align}
\end{definition}
\hfc{I think the order of the variables given to Alice doesn't matter, because
the linear system is binary.}
A widely-used example of a linear system game is the Magic Square game introduced in Ref.~\cite{magic_square}, which 
have equations
\begin{align*}
    &x_1 + x_2 + x_3 = 0 && x_4 + x_5 + x_6 = 0 &&
    x_7 + x_8 + x_9 = 0 \\
    &x_1 + x_4 + x_7 = 0 && x_2 + x_5 + x_8 = 1 &&
    x_3 + x_6 + x_9 = 0.
\end{align*}
\hf{Note that the equations above are taken modulo $2$.
We follow this convention in the rest of our work.}
For the formulation of a general linear system games over $\Z_d$, we refer to Section $3.1$ of Ref.~\cite{coladan2017}.

@@

From the group $\Gamma$ we can construct the binary linear system game $\LS(r)$. Basically,
we associate a variable $x(s)$ to each generator $s \in S$.
Then each linear relation in $R$ can be translated to a linear equation.
For example, the linear relation $f_0f_1f_2 = e$ is translated to the equation $x(f_0) + x(f_1) + x(f_2) = 0$, and the relation 
$f_1g_1m_2 = J$ is translated to the equation
$x(f_1) + x(g_1) + x(m_2) = 1$. 
The complete list of the equations is given in \cref{def:lsg_eq}.
\begin{definition}
\label{def:lsg}
The linear system game $\LS(r)$ consists of
\begin{align*}
    & \calX^{\LS} = \{I_i\}_{i=1}^{\mr}, \\
    & \calY^{\LS} = \{ x(s) : s \in S \},
\end{align*}
where $I_i = \{ s : H(i,s) = 1\}$ is the set of all the nonzero coefficient of equation $i$
and $\mr := 14r + 62$ is the number of equations.  
\carl{Since you are defining Alice's inputs to be subsets of S, why don't you just define Bob's inputs to be elements of S? Also, again you need to account that
$J$ is an element of $S$.}
\hfc{I think setting $\calY = S$ will cause confusion.
You can see the forms of the equations in \cref{def:lsg_eq}.
If I set the question set to be $S$, the reader will confuse the 
linear equations with linear relation.
I have moved $J$ out of $S$.}
Details of $I_i$ for $1 \leq i \leq \mr$ can be found in \cref{def:lsg_eq}.
The answer sets are 
\begin{align*}
    \calA^{\LS} = \Z_2^{3} && \calB^{\LS} = \Z_2,
\end{align*}
because $|I_i| = 3$ for all $i$.
The probability distribution is uniform over all the pairs $(I_i, x(s))$ such that $s \in I_i$, so
\begin{align*}
    \pi^{\LS}(I_i, x(s)) = 
    \begin{cases}
        1/N(r) & \text{ if } s \in I_i \\
        0 & \text{otherwise,}
    \end{cases}
\end{align*}
where $N(r) := 157r + 685$ is the total number of valid question pairs.
We define $X_i := \{ \ba \in \Z_2^3: \sum_{j=1}^3 a(j) = c(i) \}$, which is the set of all the valid answers of equation $i$.
Given an answer $(\ba,b)$ for question $(I_i,x(s))$, 
the score function is
\begin{align*}
    V^{\LS}(\ba, b, I_i, x(s)) = 
    \begin{cases}
        1 \text{, if } \ba \in X_i \text{ and } a(s) = b\\
        0 \text{, otherwise}.
    \end{cases}
\end{align*}
\end{definition}
\hfc{Rewritten.}
The construction of $\LS(r)$ proves the following theorem.
\begin{theorem}
	The group $\Pg$ can be embedded in the solution group of a binary linear system game which has
	$\nr := 16r+75$ variables and $\mr := 14r + 62$ equations, where each equation has $3$ variables.
\end{theorem}
\hf{Note that when $\LS(r)$ is played between Alice and Bob, the total
number of equation and variable pairs is $N(r)$ is of order $\Theta(r)$.}

>>>>

\begin{abstract}
	We show that for any prime odd integer $d$ with primitive $r$, there exists a correlation of size
	$\Theta(r^2)$ 
	that can robustly self-test a maximally entangled state of dimension $4d-4$. Our result is
	inspired by the robust self-testing result by Bamps and Pironio (\textit{Physical Review A} $91.5$ $(2015)$) and
	techniques introduced by Slofstra (\textit{Forum of Mathematics, Pi}. Vol. $7$, $2019$). Since there are
	infinitely many prime numbers with primitive root at most $5$ (\textit{The Mathematical Intelligencer} $10.4$ ($1988$)), 
	our result implies that constant-sized correlations are sufficient for robust self-testing of maximally entangled states
	with unbounded local dimension.
\end{abstract}
%========================================
\section{Introduction}
\label{sec:intro}
%========================================
Self-testing is a unique phenomenon of quantum mechanics.
It is also powerful because only classical interactions are required.
It has many applications in quantum
delegated computation \cite{ruv2013,coladan2017verifier} and device independent quantum cryptography
\cite{mayersyao,vv2014,miller2017,fu2018,eat2018}.

The case of self-testing $2$-dimensional EPR pair, which is defined by
\begin{align*}
    \ket{EPR} = \frac{1}{\sqrt{2}}(\ket{00}+\ket{11}),
\end{align*}
is fully understood.
The techniques for robustly self-testing $\ket{EPR}$ is 
first introduced in Ref.~\cite{mckague2012}, then improved in Ref.~\cite{bamps2015}. 
Ref.~\cite{yang2013} proved an generalized swap-isometry
that can be used to robustly self-test large dimensional maxially entangled states.
Its ideas are realized later in Ref.~\cite{coladan2017all}, 
which proved that all pure bipartite entangled state 
can be self-tested.
The authors constructed a family of correlations such
that each partially or maximally entangled state of any local dimension has
a self-testing correlation in this family.
% One can also self-test many copies of the $2$-dimensional EPR
% pair in parallel \cite{mckague2016,natarajan2017,coladan2016parallel}.
% The most efficient way uses $O(\log n)$ bits question and
% answers to self-test $n$ copies of $2$-dimensional EPR
% pair \cite{lowdegree}.
% Self-testing general $d$-dimensional EPR pairs is a harder task.
% Coladangelo, Goh and Scarani has shown that all pure bipartite entangled states can be self-tested \cite{coladan2017all}
To generate a correlation in the family, Alice and Bob
have constant number of measurement settings but each 
measurement setting has the same number of outcomes as
the local dimension of the entangled state to be self-tested. 
In other words, their correlation is of size $\Theta(d^2)$,
where $d$ is the local dimension of the entangled state.
This is the only result about self-testing the general $d$-dimensional entangled state so far.
However, proving the robustness of the family of correlations remains an open problem. 
Without robustness, we cannot infer anything about a quantum strategy if
the produced correlation deviates from the ideal correlation, no matter how small the 
deviation is.

A natural question to ask is whether maximally entangled states with large local dimension
can be robustly self-tested with constant-sized correlations. 
In this paper, we give an affirmative answer to this question by proving the following theorem.
\begin{theorem}[Informal]
\label{thm:inf}
	There exists an infinite-sized set $D$ of odd prime numbers such that, for any $d \in D$, 
	the maximally entangled state of local dimension $4(d-1)$ can be robustly self-tested 
	with constant-sized question and answer alphabets.
\end{theorem}
The formal statement of this theorem is given in \cref{thm:self-test} and \cref{thm:infty}.

The set $D$ is, specifically, the set of all 
odd prime numbers whose smallest primitive root is either $2$, $3$, or $5$.  
It has been shown that this set has infinitely many elements \cite{murty1988}.
To prove \cref{thm:inf}, we construct a correlation of size $\Theta(r)$ 
for each $d \in D$ whose smallest primitive root is $r$.
This correlation is denoted by $\fC(d,r)$.
Note that although the size of $\fC(d,r)$ does not depend on $d$, the entries of $\fC(d,r)$ do.
Then we prove the robust self-testing property of $\fC(d,r)$ by showing 
that if some quantum strategy can approximate $\fC(d,r)$, then
the generalized swap isometry \cite{yang2013}
can produce the desired maximally entangled states when applied to the unknown state used in the strategy.
%Then the self-testing property of this correlation is 
%given in the following theorem.
%\begin{theorem}[Informal]
%\label{thm:pr_2}
%	All maximally entangled state with local dimension $d-1$, where $d$ is prime and has
%	primitive root $r \in \{2, 3, 5\}$, can be self-tested by a constant-sized correlation.
%\end{theorem}
\carl{The paper \cite{bamps2015} says that the earlier paper \cite{yang2013} has ``flaws.'' Check what those flaws are, and make sure that they won't put a shadow on anything that you're discussing when you cite \cite{yang2013}.} 
\hfc{The flaws are in the self-testing proof, not in the 
proof about the generalized isometry.}

The correlation $\fC(d,r)$ contains the ideal correlation of a specially-designed binary linear system game.
In a general linear system game, Alice is given a random equation 
from a linear system and she
should give an assignment of the equation.
Bob is asked to assign a value to a random variable of that equation.
They win the game if Alice's assignment satisfies the equation and Bob's
assignment to the variable matches Alice's assignment.
A widely-used and thoroughly-studied example of a linear system game is
the Magic Square game \cite{magic_square}.
In this game, the linear system is
\begin{align*}
    &x_1 + x_2 + x_3 = 0 && x_4 + x_5 + x_6 = 0 &&
    x_7 + x_8 + x_9 = 0 \\
    &x_1 + x_4 + x_7 = 0 && x_2 + x_5 + x_8 = 1 &&
    x_3 + x_6 + x_9 = 0.
\end{align*}
Using two copies of the maximally entangled state
\begin{align*}
    \ket{EPR} = \frac{1}{\sqrt{2}}(\ket{00}+\ket{11}),
\end{align*}
the Magic square game can be won
with certainty.
It has been shown that if a strategy that can win this game almost perfectly, the shared state must be close to $\ket{EPR}^{\x 2}$ up to some local isometry \cite{wu2016}, 
so we can say that the Magic Square game can robustly self-test $\ket{EPR}^{\x 2}$.
The key observation that leads to the self-testing proof is that 
a winning strategy must contain observables $X$ and $Z$ that 
satisfy the anti-commutation relation 
\begin{align*}
    X Z = - Z X.
\end{align*}
Intuitively, we can think of the Magic Square game as a way to enforce the
anti-commutation relation.

Our linear system game is designed to enforce the relation 
\begin{align*}
    U O U\ct = O^r,
\end{align*}
for some integer $r$,
in the sense that the winning strategy contains binary observables
$M_1, M_2, M_3, M_4$ on Alice's side and 
$N_1, N_2, N_3, N_4$ on Bob's side such that 
\begin{align*}
    U = M_3M_4 = N_3N_4 && O = M_1M_2 = N_1N_2.
\end{align*}
This relation implies the eigenvalue of $O$ must be $\omega_d^j = e^{ij2\pi/d}$ for some $j \neq 0$ and some prime $d$ whose primitive root
is $r$. It also implies that $U$ is a permutation of the eigenbasis of $O$.
Winning this linear system game implies that Alice and Bob share a state
$\ket{\psi}$ such that
\begin{align*}
    O \x O \ket{\psi} = \ket{\psi}, && 
    U \x U \ket{\psi} = \ket{\psi}.
\end{align*}
These two relations are important for the self-testing argument
because
the relation $O \x O \ket{\psi} = \ket{\psi}$ implies that $\ket{\psi}$
is spanned by tensor products of states in the eigenbasis of $O$;
and $U \x U \ket{\psi} = \ket{\psi}$ implies that $\ket{\psi}$ is invariant
under the permutation induced by $U$. 
At this point, the eigenvalues of $O$ are unknown, so
further restricting the eigenvalues of $O$ requires another test, 
which will be introduced later.

The special feature of our linear system game is that the sizes
of the question sets for Alice and Bob are of order $\Theta(r)$,
and the answer sets are of size $\Theta(1)$.
Restricting $r \leq 5$ in our theorem implies that our linear system 
game only uses constant-sized question sets and constant-sized answer sets.
\carl{A reader may get lost at the last sentence -- you're jumping into the material too quickly without enough explanation.}
\hfc{Rewritten.}
% The number of variables and the number of equations of the linear system game depend linearly on $r$,
% which makes our correlation of size $\Theta(r^2)$.
% Unlike previous self-testing proofs, which try to enforce the anti-commutation relation
% $XZ = \omega_d^{-1} ZX$ between Pauli operators of dimension $d \geq 2$, 
% our approach is more succinct in terms of the size of the correlation but at a cost that
% it only works for odd prime $d$.
% The reason why we focus on this relation is that if we can certify that $O$ has one eigenvalue $\omega_d$
% for some $d$ with primitive $r$,
% then it guarantees that $O$ has eigenvalues $\omega_d^j$ for $j = 1 \dots d-1$ and $U$ only
% permutes the eigenvectors of $O$ in certain way.
% After knowing the eigenvalues of $O$, we can use infer the structure of the shared state $\ket{\psi}$
% based on the two relation of $\ket{\psi}$ imposed by the linear system game --
% $U_A \x U_B \ket{\psi} = \ket{\psi}$ and $O_A \x O_B \ket{\psi} = \ket{\psi}$.
% The two relations imply that $\ket{\psi}$ is spanned by eigenvectors of $O$ and its
% Schmidt coefficient follows some pattern that is invariant under the permutation by $U$.
% At this point, we can use the generalized swap isometry \cite{yang2013} to extract a copy of the 
% $(d-1)$-dimensional maximally entangled state. Note that our robust self-testing proof 
% follows a different line of arguments from what was originally
% proposed in Ref.~\cite{yang2013}.

The remaining question is how to certify a particular eigenvalue of $O$, so we
design a nonlocal test called the extended weighted CHSH test.
% Before going to the answer,
% we remark that 
% the other specialty of the linear system game is that it forces Alice and Bob to have binary observables
% whose products are the special unitaries $U$ and $O$, because the answers to the questions of the 
% linear system games are binary. 
% The idea of decompose the unitaries of arbitrary order into binary observables was also first introduced by Slofstra \cite{slofstra2017}.
% We use a different way to decompose the unitaries, which can be seen as the inverse of Jordan's lemma, 
% The fact that Alice and Bob only have binary observables make it easier for us 
% to compose the linear system game with another nonlocal test, which we call the extended weighted CHSH test.
The difference between a nonlocal game and a nonlocal test will be discussed later.
It is designed based on the $\alpha$-weighted CHSH inequality, which is defined by
\begin{align*}
    \I_\alpha = \alpha\ip{M_1N_1}+\alpha\ip{M_1N_2} + \ip{M_2N_1} - \ip{M_2N_2}\leq 2|\alpha|,
\end{align*}
where $M_x$ and $N_y$ for $x,y \in \{1, 2\}$ are some binary observables.
Define $\mu = \arctan(1/\alpha)$,
\begin{align*}
    \pauliz = \ketbra{0}{0} - \ketbra{1}{1} && \paulix = \ketbra{0}{1} + \ketbra{1}{0},
\end{align*}
which are the Pauli-Z and Pauli-X operators.
This inequality is maximally violated when the shared state is $\ket{EPR}$,
Alice's binary observables are
\begin{align*}
    M_1 = \pauliz && M_2 = \paulix,
\end{align*}
and Bob's binary observables are
\begin{align*}
    N_1 = \cos(\mu) \pauliz+ \sin(\mu) \paulix  && N_2 = \cos(\mu) \pauliz - \sin(\mu) \paulix。
\end{align*}
We first prove that the maximal violation of $\I_\alpha$ can robustly self-test the shared
state $\ket{\psi}$ and the observables $M_1, M_2$ and $N_1, N_2$.
Then we noticed that 
\begin{align*}
    N_1N_2 = \cos(2\mu) \1  - \sin(2 \mu) \pauliz \paulix 
\end{align*}
has eigenvalues $e^{i 2\mu}$ and $e^{-i 2\mu}$.
Hence, in the extended weighted CHSH test, we set $\alpha = \cot( -\pi/d )$
for some odd prime $d$ whose primitive root is $r$,
and ask Alice and Bob
to reuse the observables $M_1, M_2$ and $N_1, N_2$，then we can certify that
the unitary $O = M_1M_2 = N_1N_2$ has eigenvalues $e^{i2\pi/d}$ and $e^{-i2\pi/d}$.
Combining this observation with the fact that $O$ satisfy the relation $UOU\ct = O^r$,
we can conclude that all the eigenvalues of $O$ are $\{ e^{ij 2\pi /d} \}_{j=1}^{d-1}$,
and the eigenspaces of all the eigenvalues have the same cardinality.
At this point, we has the explicit structure of $O$, so we 
can use the relations $U \x U \ket{\psi} = \ket{\psi}$ and $ O \x O \ket{\psi} = \ket{\psi}$
to prove the correlation $\fC(r, d)$ can robustly self-test 
a maximally entangled state of dimension $4(d-1)$.

\carl{This paragraph (also) will need more context.}
\hfc{Rewritten.}

Our contributions are four-fold.
\begin{enumerate}
    \item We identify the constant-sized question and answer sets that can be used to robustly self-test
    maximally entangled states with unbounded dimensions. Before our work, the most efficient way
    was to use $O(\log d)$-sized question and answer sets to robustly self-test
    the maximally entangled state of dimension $d = 2^n$ \cite{lowdegree}.
    \item Our self-testing proof demonstrate a new way to apply the generalized swap-isometry
    proposed in Ref.~\cite{yang2013} to robustly self-test a maximally entangled state of large lcoal
    dimension. This is the first application of the generalized swap-isometry in the robust self-testing proof.
    We believe it can be applied to prove the family of correlations proposed in Ref.~\cite{coladan2017all}
    are also robust.
    \item We demonstrate how to enforce relations between operators of large but fixed dimension in a 
    binary linear system game. Before our work, only the anti-commutation relation between $2$-dimensional
    Pauli operators can be enforced in a binary linear system game.
    \item Our result gives us deeper understanding of the set of quantum correlations.
    In previous works that proved the non-closeness of the set of quantum correlations
    \cite{slofstra2017}, 
    lower bounds of the entanglement required to achieve certain correlations are identified.
    Our work discovers a large family of correlations where we know exactly the amount of entanglement
    required to achieve each of the correlations in this family. 
\end{enumerate}

@@

A quantum strategy of a nonlocal game or a nonlocal test presented in terms of projective measurements
consists of projective measurements $\{\{M_x^a\}_{a \in \calA_x} \}_{x \in \calX}$ on Alice's side, 
$\{\{N_y^b\}_{b \in \calB_y} \}_{y \in \calY}$ on Bob's side, and a shared state $\ket{\psi}$. 
By projective measurements, we mean that  
$(M_x^a)^2 = M_x^a = (M_x^a)^\dagger$ and $(N_y^b)^2 = N_y^b = (N_y^b)^\dagger$.
Then Alice and Bob's quantum strategy produces the conditional probability distribution
\begin{align}
	\pr{ab}{xy} = \bra{\psi} M_x^a \x N_y^b \ket{\psi},
\end{align}
for each $(x,y) \in \calX \times \calY$ and $(a,b) \in \calA_x \times \calB_y$.
Note that the tensor product structure indicates that the
two parties cannot communicate with each other, which is the reason why such game is called a nonlocal game.
For simplicity we omit the tensor product symbol between operators acting on different Hilbert spaces in the rest of the work, so if $M_x^a : \calH_A \rightarrow \calH_A$ and $N_y^b: 
\calH_B \rightarrow \calH_B$, then $M_x^a N_y^b: \calH_A\x \calH_B \rightarrow \calH_A \x \calH_B$.
\begin{definition}
	Given input alphabets: $\calX$ and $\calY$, and families of output
	alphabets: $\{\calA_x\}_{x \in \calX}$ and $\{\calB_y\}_{y \in \calY}$, a correlation is a family of conditional probability distributions
	$\{\pr{ab}{xy}: a \in \calA_x, b \in \calB_y\}_{x \in \calX, y \in \calY}$.  
\end{definition}
A particular type of nonlocal games that we are interested in is called binary linear system games.
\begin{definition}[Binary linear system game]
 Let \hf{$Hx = c$} be an $m \times n$ system of linear equations over $\Z_2 = \{0, 1\}$ (meaning that $H$ is an $m$-by-$n$ matrix with entries in $\Z_2$ and 
 $c$ is a length-$n$ vector with entries in $\Z_2$). 
 The associated linear system game involves two
 players Alice and Bob. 
 The input and output alphabets are 
 \begin{align*}
     \calX = \{I_i\}_{i=1}^m && &\calY = \{1 \dots n\} \\
     \calA_{I_i} = (\Z_2)^{I_i} && &\calB = \Z_2,
 \end{align*}
 where $I_i = \{j : H(i,j) = 1\}$.
 When Alice and Bob answer with $\ba$ and $b$ for questions $I_i$ and
 $j$ respectively,
 the scoring functions are defined by
 \begin{align}
 	V_{(I_i,j)}(\ba, b) =
	\begin{cases}
		1, \quad \text{if } \sum_{k \in I_i} H(i,k) a(k) \equiv c(i) \pmod 2 \text{ and } a(j) = b \\
		0,  \quad \text{otherwise.}
	\end{cases}
\end{align}
\end{definition}

A widely-used example of a linear system game is the Magic Square game introduced in Ref.~\cite{magic_square}, which 
have equations
\begin{align*}
    &x_1 + x_2 + x_3 = 0 && x_4 + x_5 + x_6 = 0 &&
    x_7 + x_8 + x_9 = 0 \\
    &x_1 + x_4 + x_7 = 0 && x_2 + x_5 + x_8 = 1 &&
    x_3 + x_6 + x_9 = 0.
\end{align*}
\hf{Note that the equations above are taken modulo $2$.
We follow this convention in the rest of our work.}
For the formulation of a general linear system games over $\Z_d$, we refer to Section $3.1$ of Ref.~\cite{coladan2017}.

@@

From the group $\Gamma$ we can construct the binary linear system game $\LS(r)$. Basically,
we associate a variable $x(s)$ to each generator $s \in S$.
Then each linear relation in $R$ can be translated to a linear equation.
For example, the linear relation $f_0f_1f_2 = e$ is translated to the equation $x(f_0) + x(f_1) + x(f_2) = 0$, and the relation 
$f_1g_1m_2 = J$ is translated to the equation
$x(f_1) + x(g_1) + x(m_2) = 1$. 
The complete list of the equations is given in \cref{def:lsg_eq}.
\begin{definition}
\label{def:lsg}
The linear system game $\LS(r)$ consists of
\begin{align*}
    & \calX^{\LS} = \{I_i\}_{i=1}^{\mr}, \\
    & \calY^{\LS} = \{ x(s) : s \in S \},
\end{align*}
where $I_i = \{ s : H(i,s) = 1\}$ is the set of all the nonzero coefficient of equation $i$
and $\mr := 14r + 62$ is the number of equations.  
\carl{Since you are defining Alice's inputs to be subsets of S, why don't you just define Bob's inputs to be elements of S? Also, again you need to account that
$J$ is an element of $S$.}
\hfc{I think setting $\calY = S$ will cause confusion.
You can see the forms of the equations in \cref{def:lsg_eq}.
If I set the question set to be $S$, the reader will confuse the 
linear equations with linear relation.
I have moved $J$ out of $S$.}
Details of $I_i$ for $1 \leq i \leq \mr$ can be found in \cref{def:lsg_eq}.
The answer sets are 
\begin{align*}
    \calA^{\LS} = (\Z_2)^{I_i} && \calB^{\LS} = \Z_2,
\end{align*}
because $|I_i| = 3$ for all $i$.
The probability distribution is uniform over all the pairs $(I_i, x(s))$ such that $s \in I_i$, so
\begin{align*}
    \pi^{\LS}(I_i, x(s)) = 
    \begin{cases}
        1/N(r) & \text{ if } s \in I_i \\
        0 & \text{otherwise,}
    \end{cases}
\end{align*}
where $N(r) := 157r + 685$ is the total number of valid question pairs.
We define $X_i := \{ \ba \in (\Z_2)^{I_i}: \sum_{s \in I_i} a(s) = c(i) \}$, which is the set of all the valid answers of equation $i$.
Given an answer $(\ba,b)$ for question $(I_i,x(s))$, 
the score function is
\begin{align*}
    V^{\LS}_{I_i, x(s)}(\ba, b) = 
    \begin{cases}
        1 \text{, if } \ba \in X_i \text{ and } a(s) = b\\
        0 \text{, otherwise}.
    \end{cases}
\end{align*}
\end{definition}
\carl{This definition does not seem consistent.  You are using $a$ both as a function on $\{ 1, 2, 3 \}$ and as a function on $S$.}
\hfc{Fixed.}
The construction of $\LS(r)$ proves the following theorem.
\begin{theorem}
	The group $\Pg$ can be embedded in the solution group of a binary linear system game which has
	$\nr := 16r+75$ variables and $\mr := 14r + 62$ equations, where each equation has $3$ variables.
\end{theorem}
\hf{Note that when $\LS(r)$ is played between Alice and Bob, the total
number of equation and variable pairs is $N(r)$ is of order $\Theta(r)$.}

\hf{The ideal strategy of $\LS(r)$ is based on
the representation $\Psi$ of $\Gamma$ defined in \cref{def:rep_gamma}
of \cref{sec:rep_gamma}.
We discuss the ideal strategy in in \cref{sec:tests}.
Here we only highlight what $a_1, a_2, a_3$ and $a_4$ are mapped to by the representation $\Psi$, along
with the important properties of the representation of these four generators,
since they are the key generators of $\Gamma$.
}
